Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-02-02 docs/ACM/paper.tex
Normalizing references.

Annotation systems have risen to a place of prominence as a simple and
effective means to write parallel programs.
Examples of such systems include OpenMP~\cite{JaegerCP15},
OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} and
Tareador~\cite{Ayguade15}.
Annotations work as a meta-language: they let developers grant parallel
semantics to syntax originally written to execute sequentially.
%\guido{What do you mean by modern accelerators? Not clear.}
Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
to substantial performance gains~\cite{Sura16Performance, Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
%\guido{Suppport what?}
Nevertheless, although convenient, the use of annotations is not straightforward, 
and still lacks supporting tools that help programmers to check if annotations
are correct and/or effective.
%replaced:
%Yet, even if convenient,

@@

Although the OpenMP runtime guarantees correctness, its scheduling policy
is heavily jeopardized by the excessive queueing up of tasks. Specifically, algorithms
such as \emph{SparseLU} and \emph{FFT} can suffer bloat because of
too many tasks in the Task Graph.  \cite{Kenjiro17}.

>>>>

Annotation systems have risen to a place of prominence as a simple and
effective means to write parallel programs.
Examples of such systems include OpenMP~\cite{JaegerCP15},
OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
OpenSs~\cite{MeenderinckJ11}, Cilk++~\cite{Leiserson09} and
Tareador~\cite{Ayguade15}.
Annotations work as a meta-language: they let developers grant parallel
semantics to syntax originally written to execute sequentially.
%\guido{What do you mean by modern accelerators? Not clear.}
Combined with modern hardware accelerators such as GPUs and FPGAs, they have led
to substantial performance gains~\cite{Martineau16, Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
%\guido{Suppport what?}
Nevertheless, although convenient, the use of annotations is not straightforward, 
and still lacks supporting tools that help programmers to check if annotations
are correct and/or effective.
%replaced:
%Yet, even if convenient,

@@

Although the OpenMP runtime guarantees correctness, its scheduling policy
is heavily jeopardized by the excessive queueing up of tasks. Specifically, algorithms
such as \emph{SparseLU} and \emph{FFT} can suffer bloat because of
too many tasks in the Task Graph\cite{Huynh17}.
